Appendix B

### 2021-10-23 manuscript.Rmd
simsem

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
r_refs("references.bib")
```

@@

@@

>>>>

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
r_refs("references.bib")
```

@@

```{r simulation, eval=FALSE, include=FALSE}
library("simsem")
pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item7+ .50*Ritem8+ .49*item9
                 F3 =~  .78*item27+ .77*item3+ .68*item40 + .13*item30 + .20*item41
                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item4+ .22*item1 
                       a1==a2
                       a3==a4
                item30 ~~ .82*item41
F1~~1*F1
F2~~1*F2
F3~~1*F3
F4~~1*F4
F5~~1*F5
"

sam.model <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                       "

sim.300 <- sim(200, model = sam.model, n =200, generate = pop.model, lavaanfun = "lavaan", auto.var =T, auto.fix.first =F, seed = 123)
summary(simulation)
summaryParam(simulation, detail =T, alpha = .05)

#power should be higher than .80, average CI width should be lower than .15
#Estimate standard error bias

SD.Bias <- (summaryParam(simulation)[3]-summaryParam(simulation)[2])/summaryParam(simulation)[3]
```

@@

```{r clean}
cleanFolder <- function() {
  answer <- NA
  while(!(answer %in% c('y', 'n'))) {
    answer <- readline(paste("Clean ", getwd(),"? (y/n)"))
  }
  if(answer == 'y') {
    rules <- c('.log', '.vrb', '.nav', '.snm', '.toc', 
               '-tikzDictionary', '.tex', '.synctex.gz')
    file.remove(list.files(pattern = paste0('\\',rules ,'$', collapse = '|')))
  }
}
```
